
\documentclass[11pt]{article}

\begin{document}
\begin{center}
\begin{Huge}
Movie Reviews
\end{Huge}
\end{center}
\section*{ 3 idiots }

Written and directed by Rajkumar Hirani, whose two previous films also tweaked Indian sensibilities with great commercial and critical success, "3 Idiots" dominated at the boxoffice. In India, the Reliance Big Pictures release collected more than 1 billion rupees (21.3 million dollars) in its first four days of release.

A great part of the film's appeal is Aamir Khan, who has come to specialize in heroic iconoclasts, such as a rebellious villager in "Lagaan" or a visionary teacher of special-needs kids in "Taare Zameen Par." As Rancho, a young engineer of dazzling inventiveness, Khan conveys smarts, mischief and, finally, compassion, as he spurs his friends on to greatness before he mysteriously disappears.

The film's good points, though, are marred by a slow start and a nerve-jangling soundtrack (except for the charming "Aal Izz Well"). Perceptive, subtle acting work by Khan, Madhavan and Joshi also clashes with buffoonish performances by Omi Vaidya, as an odious school rival, and veteran character actor Irani, whose character is cursed with an unnecessary -- and unfunny -- lisp.


Hirani's screenplay also jumps back and forth in time over a 10-year period with limited success, leaving the viewer often wondering whether we're seeing scenes set in the present or the past.



\section*{ Chak de! India}
While we continue to go into ecstasy over cricket we hardly seem to realize that hockey is the true-blue Indian game. Chak De India aims at giving the dying game the respect it deserves.

As far as the success of the movie is concerned a lot is at stake. Sport is not a very successful genre in Bollywood, most sport based movies have failed miserably at the box office. The only exception being Aamir Khan’s oscar nominated Lagaan. Also the last two Yash Raj Films, Ta Ra Rum Pum and Jhoom Barabar Jhoom disapponted.

So with a lot at stake the Yashraj – SRK combo deliver and deliver big time.

Chak De India directed by Shimit Amin (Ab Tak Chapan) and produced by Aditya Chopra (Yash Raj Films) is about an ex Indian Hockey team captain?s return as the Coach to the Indian Women?s National Hockey team and his fight in making team India a strong and indomitable team.

Kabir Khan (Shah Rukh Khan) is a man who overcomes the problems in life without being skeptical and disturbed. He isn?t an outsider to the game of hockey as he had once led the Indian Hockey team and unfortunately experienced failure and disgrace. He approaches to be the coach of a rag-tag bunch of girls as a challenge to overcome his failure and the obstacles that had once stopped him from taking India to the top league in the field of Hockey.

Kabir?s challenge lied in reshaping a team which in pursuing their personal goals had forgotten what it is like to play as a team. His challenge lied not in training or honing the skills of the team but rather to bring them together as a team and instill the virtue of belief. A belief in realizing that if you want, you can do it! His mantra was ?Jo nahin ho sakta hai, wahi to karna hai.. ” Will he succeed in making his team by overcoming their diverse backgrounds and striking away all the bitterness, by learning to use everything that life hurls on them as a secret weapon?

Director Shimit Amin has taken an interesting leap in style, substance, conceit and stardom. From Nana Patekar an encounter specialist in “Ab Tak Chhappan” to Shah Rukh playing a coach who transforms a team of rag-tag girls into champions.

With a strong screenplay, Shimit’s direction is first rate. He has ensured there isnt even a single dull moment. Every scene makes a impact. Also the feel of the movie is so real that it makes you cheer and pray for the team to win. The background music is brilliant so is the cinematography.

Performances – Shahrukh Khan is the heart and soul of Chak De India. He has just delivered arguably his best performances in his career. It fills your heart with happiness to see the actor in Shahrukh in full form. He portrays the role of Hockey coach with a lot of dignity, intensity and charm. Undoubtedly the best performance of the year.

The team of girls are exceptionally good. Characters of Preethi and Komal stand out.

Overall, this is a must watch for every Indian. The performances, the screenplay, the direction are just perfect. You cant ask or expect more. Is there a negative? Yup, the intermission.. It makes you restless!! At the box office, its undoubtedly going to create history.
\end{document}
